Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-10-07 Ben_Manuscripts/structure_paper/supporting_information.tex
Comments on supporting information.

	\item \textit{Create monomer structure file with connectivity} : We
	drew atomistic structures using MarvinSketch
	17.13~\cite{chemaxon_marvinsketch_2017} with all hydrogen atoms drawn out
	explicitly. We optimized the 3D geometry of the structure using the `Clean in
	3D' function of MarvinSketch.  We saved the structure as a .mol file, then
	converted it to .pdb format using Open Babel 2.4.1
	\cite{oboyle_open_2011,noauthor_open_nodate}.

	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}} : Using
	the .pdb structure file as input, we ran
	\texttt{antechamber}~\cite{wang_automatic_2006} using the AM1-BCC charge model.
	The net charge on the monomer is input as -1 since the sodium ion is kept as 
	a separate residue. We use \texttt{LEaP}~\cite{case_ambertools16_2016} and the
	output of \texttt{antechamber} to create Amber topology files. A detailed
	tutorial can be accessed elsewhere \cite{walker_antechamber_nodate}.

	\item \textit{Create GROMACS topologies from Amber output} : The output
	of \texttt{LEaP} is a .inpcrd and a .prmtop file which are Amber topology
	files. Using acpype.py \cite{sousa_da_silva_acpype_2012}, we converted the
	\texttt{LEaP} output into GROMACS .gro and .top files.

	\item \textit{Perform a simulated annealing procedure on the monomer} :
	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
	editconf}. The monomer was centered in the box with edges of the
	box spaced at least 3 nm from the monomer on all sides. We ran an energy minimization
	on the system with the steepest descent algorithm. Next we performed an NVT
	simulated annealing procedure. We linearly decreased the temperature of the
	system from 1000 K to 50 K over the course of 10 ns. We randomly chose a monomer
	configuration from the last 10 \% of the trajectory.

@@

	\item \textit{Anneal again to get final structure} : We repeated the
	same simulated annealing procedure using the monomer topology with
	\texttt{molcharge} charges. A random monomer configuration was pulled from the
	last 10 \% of the trajectory and was used to build all assemblies reported
	(Figure~\ref{fig:monomer}).

@@

  We used the same number of monomers (400) that we used in all other simulations. 
  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
  box with a volume of 660 $nm^3$, 25\% larger than those used to create ordered unit
  cells we studied. We tested systems with semi-isotropic and anisotropic pressure 
  coupling since the shape of the unit cell will likely need to change in order to 
  accommodate hexagonally packed pores.

@@

  We chose to build all systems using 20 monomers per column. We made this choice
  by considering a number of factors that directly affect the quality of our results. 
  Clearly, choosing a small number of layers will cause the system to suffer from 
  finite size effects. Even in our 20 monomer-per-column system, axial correlations
  between stacked monomers persist throughout the entire correlation function (see
  Figure~\ref{M-fig:correlation} of the main text). The correlation function of the system which we
  built with 40 monomers per column is very similar to that created with 20 monomers
  per columns (continues to oscillate for its full length
  (Figure~\ref{fig:tall_correlation_full})). If we continue adding monomers, the 
  correlation function will eventually fully decay but it is not worth the 
  computational expense. Regardless, the correlation lengths calculated from 20
  monomer per column simulations are in sufficient agreement with experiment.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{z_correlation_overlay.png}
  \caption{}\label{fig:z_correlation_overlay}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{tall_correlation_full.png}
  \caption{}\label{fig:tall_correlation_full}
  \end{subfigure}
  \caption{(a) The correlation functions generated from ordered basin sandwiched 
  configurations are nearly the same when the $z$-dimension of the system is doubled.
  (b) Oscillations persist throughout the length of the correlation function for the
  sandwiched system in the ordered basin built with 40 monomers per column. The full
  system is ca. 17 nm tall so the full correlation function covers half this length
  since periodicity forces the remaining length to be its mirror image.}\label{fig:correlation_functions}
  \end{figure}

@@

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
	than the experimental value. This systems exhibits the smallest response to our 
 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
        value for all our simulations in the main text.
        %The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
	%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
	%pore spacing. We chose to use this value for all our simulations in the main
	%text.

	\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20 \%
	larger than the experimental value. Once the restraining potential reaches 56
	kJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
	a linear trend (Figure~\ref{fig:p2p_50}).
%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
%		There is a large
 %               uncertainty with this value because, again, the array of pores deviates from 
 %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
   %             response.

@@

 %BJC: is it really necessary to explain this if I release the code? I don't explain
 %any of the other stats I calculate. 
  We are interested in 5 pore-to-pore distances which should all be
  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
  the 5 distances are independent. We can calculate a trajectory of spacing
  versus time for each of the 5 distances. We calculated the average pore-to-pore
  spacing and its uncertainty according to the following procedure:
   \begin{enumerate}
	\item We calculated the time when each of the pore-to-pore distances
	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
	after the largest of the five values.
	\item We calculated how long it takes for the data in each of the 5
	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. 
	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
	five sub-trajectories of pore-to-pore spacings.   
	\item We generate statistics using the bootstrapping technique. For
	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
	sampling from the trajectory blocks. 
	\item The average pore-to-pore distance is the mean of all pore
	spacings among all bootstrap trials.
	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
	pore spacing for each pore over all bootstrap trials. Using the 5 average 
	pore-to-pore distances, we calculate the spread with:
	\begin{equation}
	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
	\label{equation:p2p_stats}
	\end{equation}
	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
	spacings.

  \end{enumerate}
  \begin{figure}[!htb]
	\centering
	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
	\caption{There are five pore-to-pore distances that are equal in a perfect
		hexagon. If each number in the diagram represents the center of a
		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
		are independent. For example, the distance from 1 to 4 is defined by
		the location of all other pore centers.}
	\label{fig:p2p_diagram}
  \end{figure}

  Alternatively, one can calculate the pore spacing as half of the $x$ and $y$
  box vectors, however this technique does not fully capture the uncertainty
  in the pore-to-pore distances.

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  System                         & Pore Spacing ($nm$) & Pore Spacing ($nm$)              \\
                                 & Pore centers        & $\dfrac{x\ box\ vector}{2}$ ($nm$) \\ 
  \midrule
  Sandwiched, Ordered            & 4.18 $\pm$ 0.13     & 4.16 $\pm$ 0.01                  \\
  Parallel Displaced, Ordered    & 4.17 $\pm$ 0.12     & 4.18 $\pm$ 0.01                  \\
  Sandwiched, Disordered         & 4.05 $\pm$ 0.14     & 4.01 $\pm$ 0.01                  \\
  Parallel Displaced, Disordered & 4.03 $\pm$ 0.07     & 4.01 $\pm$ 0.01                  \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing measured in two ways agree within uncertainty. In the main
  text, we report values calculated by measuring the average distance between pore centers. 
  Alternatively, one can estimate the pore spacing as half of the $x$ and $y$ box vectors.
  Both methods agree within uncertainty, but measuring the distance between pore centers
  does a better job of showing the spread of pore-to-pore distances.}~\label{table:p2p}
  \end{table}

@@

  In the main text, we calculated ionic conductivity using the Nernst-Einstein 
  relationship. We also measured ionic conductivity using a second method, 
  termed the Collective Diffusion model, for robustness. The collective 
  diffusion model measures the movement of the collective variable, Q, which
  is defined as the amount of charge transfer through the system and can be 
  thought to represent the center of charge of the system. The conductance, 
  $\gamma$, of the system can be calculated as:
  \begin{equation}
	 \gamma = \dfrac{D_Q}{k_b T} 
	\label{eqn:collective_diffusion}
  \end{equation}
  $D_Q$ is the diffusion coefficient of the collective variable Q and is 
  calculated using the Einstein relation. We convert the resulting value
  to ionic conductivity by multiplying by channel length and dividing by
  the membrane cross sectional area. One can access a detailed derivation of 
  the model elsewhere\cite{liu_collective_2013}.

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{tilt_cat.png}
  \caption{As we reduce the force constants applied to the end of each
  tail of an initially tilted monomer configuration, the average tilt 
  angle with respect to the membrane plane decreases until it is nearly
  negligible.}\label{fig:tail_tilt}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_stds.pdf}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_means.pdf}
  \caption{}\label{fig:offset_ensemble_means}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_regional_density.pdf}
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered sandwiched system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
  system trajectory (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble (histogram). The mean values of $z$
  are necessarily 0 so they are not plotted. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{carboxylate_dihedral_rb.png}
  \caption{A potential energy diagram for the dihedral angle about the carbon-carbon bond of
  a carboxylate group attached to an aromatic ring, using parameters from the generalized amber 
  forcefield. It is energetically favorable for the carboxylate group to stay in plane with 
  the aromatic ring. There is a large energy penalty as the dihedral becomes antiparallel to 
  the plane of the aromatic ring.}\label{fig:carboxylate_dihedral_rb}
  \end{figure}

>>>>

	\item \textit{Create monomer structure file with connectivity}: We
	drew atomistic structures using MarvinSketch
	17.13~\cite{chemaxon_marvinsketch_2017} with all hydrogen atoms drawn out
	explicitly. We optimized the 3D geometry of the structure using the `Clean in
	3D' function of MarvinSketch.  We saved the structure as a .mol file, then
	converted it to .pdb format using Open Babel 2.4.1
	\cite{oboyle_open_2011,noauthor_open_nodate}.

	\item \textit{Assign GAFF atomtypes using \texttt{antechamber}}: Using
	the .pdb structure file as input, we ran
	\texttt{antechamber}~\cite{wang_automatic_2006} using the AM1-BCC charge model.
	The net charge on the monomer is input as -1 since the sodium ion is kept as 
	a separate residue. We use \texttt{LEaP}~\cite{case_ambertools16_2016} and the
	output of \texttt{antechamber} to create Amber topology files. A detailed
	tutorial for using \texttt{LEaP} for parameterizationcan be accessed elsewhere \cite{walker_antechamber_nodate}.

	\item \textit{Create GROMACS topologies from Amber output}: The output
	of \texttt{LEaP} is a .inpcrd and a .prmtop file which are Amber topology
	files. Using acpype.py \cite{sousa_da_silva_acpype_2012}, we converted the
	\texttt{LEaP} output into GROMACS .gro and .top files.

	\item \textit{Perform a simulated annealing procedure on the monomer}:
	We created a cubic box around the monomer using the GROMACS command \texttt{gmx
	editconf}. The monomer was centered in the box with edges of the
	box spaced at least 3 nm from the monomer on all sides. We ran an energy minimization
	on the system with the steepest descent algorithm. Next we performed an NVT
	simulated annealing procedure. We linearly decreased the temperature of the
	system from 1000 K to 50 K over the course of 10 ns. We randomly chose a monomer
	configuration from the last 10\% of the trajectory.

@@

	\item \textit{Anneal again to get final structure}: We repeated the
	same simulated annealing procedure using the monomer topology with
	\texttt{molcharge} charges. A random monomer configuration was pulled from the
	last 10\% of the trajectory and was used to build all assemblies reported
	(Figure~\ref{fig:monomer}).

@@

  We used the same number of monomers (400) that we used in all other simulations. 
  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
  box with a volume of 660 nm$^3$, 25\% larger than those used to create ordered unit
  cells we studied. We tested systems with semi-isotropic and anisotropic pressure 
  coupling since the shape of the unit cell will likely need to change in order to 
  accommodate hexagonally packed pores.

@@

  We chose to build all systems using 20 monomers per column, i.e. for a simulation with 5 columns around each pore, there are 100 monomers per pore, and 400 monomers per simulation.  We made this choice
  by considering a number of factors that directly affect the quality of our results. 
  Clearly, choosing a smaller number of layers will cause the system to suffer from 
  larger finite size effects. Even in our 20 monomer-per-column system, axial correlations
  between stacked monomers persist throughout the entire correlation function (see
  Figure~\ref{M-fig:correlation} of the main text). The correlation function of the system which we
  built with 40 monomers per column is very similar to that created with 20 monomers
  per columns (continues to oscillate for its full length
  (Figure~\ref{fig:tall_correlation_full})). If we continue adding monomers, the 
  correlation function will eventually fully decay but it is not worth the 
  computational expense. We do find that the correlation lengths calculated from 20
  monomer per column simulations are in sufficient agreement with experiment. 
  %MRSF: if 10 monomers per column gave inconsistent pores when tried, might as well mention that here. 
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{z_correlation_overlay.png}
  \caption{}\label{fig:z_correlation_overlay}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{tall_correlation_full.png}
  \caption{}\label{fig:tall_correlation_full}
  \end{subfigure}
  \caption{(a) The correlation functions generated from ordered basin sandwiched 
  configurations are nearly the same when the $z$-dimension of the system is doubled.
  (b) Oscillations persist throughout the length of the correlation function for the
  sandwiched system in the ordered basin built with 40 monomers per column. The full
  system is ca. 17 nm tall so the full correlation function covers half this length
  since periodicity forces the remaining length to be its mirror image.}\label{fig:correlation_functions}
  \end{figure}

@@

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10\% larger
	than the experimental value. This systems exhibits the smallest response to our 
 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
        value for all our simulations in the main text.
        %The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
	%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
	%pore spacing. We chose to use this value for all our simulations in the main
	%text.

	\item 50 \AA~: We tested a pore spacing of 50 \AA, about 20\%
	larger than the experimental value. Once the restraining potential reaches 56
	kJ mol$^{-1}$ nm$^{-2}$, the pore spacing begins to decrease rapidly, following
	a linear trend (Figure~\ref{fig:p2p_50}).
%		After 400 ns, the average pore spacing is 4.37 $\pm$ 0.13 nm.
%		There is a large
 %               uncertainty with this value because, again, the array of pores deviates from 
 %               hexagonal character. Using Figure ~\ref{fig:p2p_diagram} as a reference, pore 
  %              2 drifts outward from the array and forces the 1-4 distance to shrink in 
   %             response.

@@

 %BJC: is it really necessary to explain this if I release the code? I don't explain
 %any of the other stats I calculate. 
  We are interested in 5 pore-to-pore distances which should all be
  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
  the 5 distances are independent. We can calculate a trajectory of spacing
  versus time for each of the 5 distances. We calculated the average pore-to-pore
  spacing and its uncertainty according to the following procedure:
   \begin{enumerate}
	\item We calculated the time when each of the pore-to-pore distances
	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
	after the largest of the five values.
	\item We calculated how long it takes for the data in each of the 5
	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. 
	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
	five sub-trajectories of pore-to-pore spacings.   
	\item We generate statistics using the bootstrapping technique. For
	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
	sampling from the trajectory blocks. 
	\item The average pore-to-pore distance is the mean of all pore
	spacings among all bootstrap trials.
	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
	pore spacing for each pore over all bootstrap trials. Using the 5 average 
	pore-to-pore distances, we calculate the spread with:
	\begin{equation}
	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
	\label{equation:p2p_stats}
	\end{equation}
	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
	spacings.
        %MRSF: I think this is the spread in a single pore, not the average pore.  Should probably make it clearer to readers which it is (i.e. uncertainty in one, not uncertainty in mean of the four).
  \end{enumerate}
  \begin{figure}[!htb]
	\centering
	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
	\caption{There are five pore-to-pore distances that are equal in a perfect
		hexagon. If each number in the diagram represents the center of a
		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
		are independent. For example, the distance from 1 to 4 is defined by
		the location of all other pore centers.}
	\label{fig:p2p_diagram}  %MRSF: this label is multiply defined. 
  \end{figure}

  Alternatively, one can calculate the pore spacing as half of the $x$ and $y$
  box vectors, however this technique does not fully capture the uncertainty
  in the individual pore-to-pore distances.

  \begin{table}[h]
  \centering
  \begin{tabular}{ccc}
  \toprule
  System                         & Pore Spacing ($nm$) & Pore Spacing ($nm$)              \\
                                 & Pore centers        & $\frac{1}{2}(x\ box\ vector)$ ($nm$) \\ 
  \midrule
  Sandwiched, Ordered            & 4.18 $\pm$ 0.13     & 4.16 $\pm$ 0.01                  \\
  Parallel Displaced, Ordered    & 4.17 $\pm$ 0.12     & 4.18 $\pm$ 0.01                  \\
  Sandwiched, Disordered         & 4.05 $\pm$ 0.14     & 4.01 $\pm$ 0.01                  \\
  Parallel Displaced, Disordered & 4.03 $\pm$ 0.07     & 4.01 $\pm$ 0.01                  \\
  \bottomrule
  \end{tabular}
  \caption{The pore spacing measured in two ways agree within uncertainty. In the main
  text, we report values calculated by measuring the average distance between pore centers. 
  Alternatively, one can estimate the pore spacing as half of the $x$ and $y$ box vectors.
  Both methods agree within uncertainty, but measuring the distance between pore centers
  does a better job of showing the spread of pore-to-pore distances.}~\label{table:p2p}
  \end{table}

@@

  In the main text, we calculated ionic conductivity using the Nernst-Einstein 
  relationship. We also measured ionic conductivity using a second method, 
  %MRSF: Don't capitalize Collective Diffusion. Also, add citation on first mention.
  termed the Collective Diffusion model, for robustness. The collective 
  diffusion model measures the movement of the collective variable, Q, which
  is defined as the amount of charge transfer through the system and can be 
  thought to represent the center of charge of the system. The conductance, 
  $\gamma$, of the system can be calculated as:
  \begin{equation}
	 \gamma = \dfrac{D_Q}{k_b T} 
	\label{eqn:collective_diffusion}
  \end{equation}
  $D_Q$ is the diffusion coefficient of the collective variable Q and is 
  calculated using the Einstein relation. We convert the resulting value
  to ionic conductivity by multiplying by channel length and dividing by
  the membrane cross sectional area. One can access a detailed derivation of 
  the model elsewhere\cite{liu_collective_2013}.

@@

  \begin{figure}[!htb]
  \centering
  % seems to be missing in the repository? tilt_cat.png
  \includegraphics[width=0.5\textwidth]{tilt_cat.png}
  \caption{As we reduce the force constants applied to the end of each
  tail of an initially tilted monomer configuration, the average tilt 
  angle with respect to the membrane plane decreases until it is nearly
  negligible.}\label{fig:tail_tilt}
  \end{figure}

@@

  %MRSF: isn't this picture the same in the main draft of the document. Probably wouldn't have occured.
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_stds.pdf}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_means.pdf}
  \caption{}\label{fig:offset_ensemble_means}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{sandwiched_ensemble_regional_density.pdf}
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered sandwiched system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
  system trajectory (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble (histogram). The mean values of $z$
  are necessarily 0 so they are not plotted. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}

@@

  %MRSF: probably needs some context, since this is for a force field, not for QM. Did you have plots for several different force fields, which all are presumably trying to capture the QM that all basically gave the same results? That would be better evidence.
  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{carboxylate_dihedral_rb.png}
  \caption{A potential energy diagram for the dihedral angle about the carbon-carbon bond of
  a carboxylate group attached to an aromatic ring, using parameters from the generalized amber 
  forcefield. It is energetically favorable for the carboxylate group to stay in plane with 
  the aromatic ring. There is a large energy penalty as the dihedral becomes antiparallel to 
  the plane of the aromatic ring.}\label{fig:carboxylate_dihedral_rb}
  \end{figure}
